Proposal: What is the impact of weather catastrophe frequency and severity on property insurance policy prices, and how can homeowners alleviate financial strain?

### 2023-10-09 proposal/proposal.tex
title changed

\title{Proposal: Something Interesting}
\author{Carol Li\\
  University of Connecticut
}

@@

\paragraph{Specific Aims}
Our study focuses on three main objectives pertaining to weather catastrophes and property insurance pricing. To start with, we seek 
to explore the overarching research query: ``What is the impact of weather catastrophe frequency and severity on home insurance policy 
prices, and how can homeowners alleviate financial strain?`` This fundamental inquiry will serve as the basis for our investigation.

>>>>

\title{Proposal: What is the impact of weather catastrophe frequency and severity on property insurance policy 
prices, and how can homeowners alleviate financial strain?}
\author{Carol Li\\
  University of Connecticut
}

@@

\paragraph{Specific Aims}
Our study focuses on three main objectives pertaining to weather catastrophes and property insurance pricing. To start with, we seek 
to explore the overarching research query: ``What is the impact of weather catastrophe frequency and severity on property insurance policy 
prices, and how can homeowners alleviate financial strain?`` This fundamental inquiry will serve as the basis for our investigation.
